Trauma treatment delay

### 2023-09-20 manuscriptlongversion.Rmd
method and code

Many hospitals, mainly in HIC, have a registry database where they log the patients information and timeline of what happened. This is important work, as a cornerstone of trauma quality improvement programs is multidisciplinary mortality and morbidity review to identify OFIs and implement corrective actions. This refers to a meeting where different specialities who work with trauma care sit down and go through cases where possible OFIs were identified by nurses who go through the trauma care quality database. These MoM conferences are very resource and time craving, which is why many hospitals doesn't have the means to perform them. In Sweden, most hospitals have mortality conferences on deceased patient cases, but only one has MoM conferences to better their trauma care on patients who lived.

Examples of opportunities for improvement may include lack of resources and management errors. One common OFI that this paper will look further into is delayed treatment. Among the preventable or possibly preventable deaths in trauma patients, a subgroup of patients determined by the Combined Trauma Death Review Committee, delay in treatment has been identified as a major error contributing to death, found in up to 52.9% of patients in said group [@Teixeira_Inaba_Hadjizacharia_Brown_Salim_Rhee_Browder_Noguchi_Demetriades_2007]. Although it is such a common OFI, the patient level factors associated with delayed treatment are poorly understood. There may be several factors that correlate with receiving delayed treatment, but they have yet to be identified. Mapping these factors may help in identifying patients that might be at risk for receiving delayed treatment before it happens.

@@

>>>>

Many hospitals, mainly in HIC, have a registry database where they log the patients information and timeline of what happened. This is important work, as a cornerstone of trauma quality improvement programs is multidisciplinary mortality and morbidity review to identify OFIs and implement corrective actions. This refers to a meeting where different specialities who work with trauma care sit down and go through cases where possible OFIs were identified. These MoM conferences are very resource and time craving, which is why many hospitals doesn't have the means to perform them. In Sweden, most hospitals have mortality conferences on deceased patient cases, but only one has MoM conferences to better their trauma care on patients who lived. Examples of opportunities for improvement may include lack of resources and management errors. One common OFI that this paper will look further into is delayed treatment. Among the preventable or possibly preventable deaths in trauma patients, a subgroup of patients determined by the Combined Trauma Death Review Committee, delay in treatment has been identified as a major error contributing to death, found in up to 52.9% of patients in said group [@Teixeira_Inaba_Hadjizacharia_Brown_Salim_Rhee_Browder_Noguchi_Demetriades_2007]. Although it is such a common OFI, the patient level factors associated with delayed treatment are poorly understood. There may be several factors that correlate with receiving delayed treatment, but they have yet to be identified. Mapping these factors may help in identifying patients that might be at risk for receiving delayed treatment before it happens.

@@

Multivariable and potentially univariable logistical regression
